---
title       : Linear regression with a selection of regressors
subtitle    : Performed on the dataset MTCARS
author      : S.Cochet 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 2

The datasets is composed of different columns: 

```{r datasets}
head(mtcars, 3)
````

During the chapter related to Regresion model, it was determined the regressors with the most influence on the dependant variable mpg (taking into consideration the ones with a Pr(>|t|)) value greater than 0.05 which  means that a limited effect of this predictor on the outcome has been oberved)

The three majors predictors are: wt (weight), am (type of transmission) and qsec (acceleration)

--- .class #id 

## Slide 3

Let's review the linear model with the three predictors:

```{r regression}
fit <- lm(mpg ~ am + wt + qsec, data = mtcars)

fit
````


Here are the results of the model with the three predictor, one can chose to identify a different combination of the predictors (two of them, one of them and view directly the effect on the coeeficients, Pr(|t|)) and adjusted R-squared

--- .class #id 

## Slide 4


By acting on the choice of predictors, one can view that the predictor weight (wt) is the one which has the maximum effect on mpg : 


  - Pr(|t|) equals 1.29 e-10 
  
  
  - Adjusted R-square equals 0.74

This predictor is a powerful one and explains 74 % of the variation of the dependant variable mpg


--- .class #id 

## Slide 5

Would you need to find the sources ?

SHINY:

app.R

SLIDIFY

index.rmd

Thanj you !